Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-06 paper/main.tex
starting to work on description of the "adaptive" condition

\subsubsection*{Adaptive conditions}

@@

\subsubsection*{Computing clustering scores and memory fingerprints}

>>>>

\subsubsection*{Adaptive condition}

We designed the \textit{adaptive} experimental condition to study the effect on
memory for information that matched (or mismatched) the ways participants
``naturally'' organized their memories of the lists they studied. Like the
other conditions, all participants in the adaptive condition studied a total of
16 lists, in a randomized order. We varied the words' colors and locations for
every word presentation, as in the feature rich and order manipulation
conditions.

All participants in the adaptive condition began the experiment by studying a
set of four \textit{initialization} lists. Words and features on these lists
were presented in a randomized order (computed independently for each
participant). These initialization lists were used to estimate each
participant's ``memory fingerprint,'' defined below. At a high level, a
participant's memory fingerprint describes how they prioritize different
semantic, lexicographic, and/or visual features when they organize their
memories.

Next, participants studied a sequence of 12 lists in three batches of 4 lists
each. These batches came in three types: \textit{random}, \textit{stabilize},
and \textit{destabilize}. The batch types determined how words on the lists in
that batch were ordered. Lists in each batch were always presented
consecutively (e.g., a participant might receive four random lists, followed by
four stabilize lists, followed by four destabilize lists). The batch orders
were evenly counterbalanced across participants: there are six possible
orderings of the three batches, and 10 participants were randomly assigned to
each ordering sub-condition.

Lists in the random batches were sorted randomly (as on the initialization
lists and in the feature rich condition). Lists in the stabilize and
destabilize batches were sorted in ways that either matched or mismatched each
participant's memory fingerprint, respectively. Our procedures for computing
participants' memory fingerprints and ordering the stabilize and destabilize
lists are described next.

\paragraph*{Computing clustering scores and memory fingerprints.}

@@

\paragraph{Temporal clustering score.}
